\chapter{Introduction}
\label{intro}

% 
% Dima recommends:
% 
% intro can list char'n of magcoll geny as a key result)
% For the intro, summarize your results (destroy sat at inacc, Mag gen & MS, magcoll charn of geny)
%   Don't go further back than Cohen. Talk about failure of CH, GCH, powerset. Easton's Thm for regs.

Ever since Cohen proved the independence of the Continuum Hypothesis from $\mathrm{ZFC}$, set theorists have greatly expanded on his method of forcing to discover ever more complex phenomena in the multiverse of set theories.

A proof or disproof of the Continuum Hypothesis ($\mathrm{CH}$), the statement that $2^{\aleph_0}=\aleph_1$, had been on mathematicians' radar since the nineteenth century, but Cohen finally proved its undecidability.
In brief, Cohen's method of forcing starts with a universe $V$ of $\mathrm{ZFC}$ and, using tools entirely within $V$, interprets a new universe with entirely new objects.
Cohen's methods allow for the creation of a universe in which $\mathrm{CH}$ holds\footnote{
%   While G\"odel's Constructible universe $L$ also achieves this, Cohen's method allows for a more uniform treatment.
}.
Furthermore, forcing with the combinatorial object $Add(\omega,1)$ can create a new universe $V^{Add(\omega,1)}$ with a real number not present in $V$.
And forcing with $Add(\omega,\omega_2)$ can create real numbers on a scale hitherto undreamt of, so much that $V^{Add(\omega,\omega_2)}\models \card{\mathcal{P}({\aleph_0})}\geq\aleph_2$.

The question then arose of whether similar independence results could hold at other cardinals, and for regular cardinals Easton quickly characterized the exact behavior of the powerset operator.
A regular cardinal $\kappa$ is one for which any $<\kappa$-sized union of $<\kappa$-sized sets is of size $<\kappa$.
For instance (under $\mathrm{ZFC}$) $\omega_1$ is regular, as is $\omega_{\alpha+n}$ for any $n<\omega$, however $\aleph_\omega$ is not, as $\aleph_\omega=\bigcup_{n<\omega} \aleph_n$.
So we say that $\aleph_\omega$ is singular, with cofinality $\cf(\aleph_\omega)=\omega$; likewise $\cf(\aleph_{\omega+\omega})=\omega$ and $\cf(\aleph_{\omega_1})=\omega_1$.

In brief, Easton showed, using Cohen's tools and a universe satisfying $\mathrm{GCH}$ (i.e. for every $\kappa$, $2^\kappa=\kappa^+$),
that the following three properties of the powerset function are the \emph{only} constraints to its behavior on regular cardinals:
\begin{enumerate}
  \item (Cantor's Theorem) $2^\kappa>\kappa$
  \item (K\"onig's Lemma) $\cf(2^\kappa)>\kappa$
  \item (Weak Monotonicity) if $\kappa\leq \lambda$ then $2^\kappa\leq 2^\lambda$
\end{enumerate}

%   For sings, much more interesting. Can't just use Cohen poset, need large cards. Magidor, from s.c. and later by Mitchell, Woodin, reduced and made optimal (to o(kappa)=kappa++).

%   We combine techniques of forcings and large cardinals, where LCs are strengthenings of ZFC, (ConZFC or Konig infinity lemma), and much stronger ones that satisfy omega-like compactness results. (Can even note that omega is in a sense a "ctble inaccessible)
%   (Mention cpctness props, incl stat refl'n for reg cards)

For the powerset at singular cardinals, the situation is far more complicated and consistency results here require large cardinals.
Here, we investigate $\mathrm{SCH}$, the principle that if $\kappa$ is a singular strong limit cardinal, then $2^\kappa=\kappa^+$.
Unlike with $\mathrm{GCH}$, Easton's method preserves $\mathrm{SCH}$.
As Silver showed, the powerset operator on large cardinals is much more restricted, in that if $\mathrm{SCH}$ fails, then the first cardinal at which $\mathrm{SCH}$ fails must have countable cofinality.
Later results by Shelah's $\mathrm{PCF}$ theory gave even stronger restrictions.
As for the necessity of large cardinals, Jensen's Covering Lemma proves that if $\mathrm{SCH}$ fails, then many large cardinal hypotheses must be consistent.

In short, a large cardinal $\kappa$ is a cardinal so large that $V_\kappa \models \mathrm{ZFC}$, in particular one whose existence proves the consistency of $\mathrm{ZFC}$.
Since $\omega$'s existence proves the consistency of $\mathrm{ZFC}-\mathrm{Infinity}$, $\omega$ may be considered \emph{almost} a large cardinal.
Several large cardinal axioms are generalizations of compactness-style phenomena holding at $\omega$.
For example, weak compactness, the principle that $\kappa$ is inaccessible and $\kappa\rightarrow(\kappa)^2_2$, is a generalization of Ramsey's theorem that $\omega\rightarrow(\omega)^2_2$.

Combining Cohen's method of forcing with large cardinals will often partially preserve some of the large cardinal's properties in the extended universe.
This following example is due to Mitchell: if $\kappa$ is weakly compact, then every stationary subset of $\kappa$ \emph{reflects}, that is, if $S\subseteq \kappa$ is stationary, then there is some $\alpha<\kappa$ such that $S\cap \alpha$ is stationary in $\alpha$.
An appropriate forcing $\mathbb{P}$ in which $V^{\mathbb{P}}\models \kappa=\aleph_2$ will preserve this stationary reflection of $\kappa$; conversely, if $\aleph_2$ satisfies this stationary reflection, then there is a sub-universe in which $\aleph_2$ is weakly compact.

As for $\lnot\mathrm{SCH}$, Magidor argued that from a supercompact cardinal $\kappa$ (a very large cardinal hypothesis), one can force $\kappa$ to be singular and $\mathrm{SCH}$ to fail at $\kappa$;
later works by Gitik, Mitchell, and Woodin optimized this result exactly to $\kappa$ measurable with $o(\kappa)=\kappa^{++}$.

%   
%   For very large cards, have a measure-like object, equiv. to j:VtoM eltary. Stronger closure properties of M (more V-like) === larger cards.
%   
%   M equiv to taking the "ultrapower"; 

Sufficiently large cardinals, such as measurable, strong, strongly compact, and supercompact cardinals, come with a highly complete ultrafilter $U$ that induces a nontrivial elementary self-embedding of the universe $j:V\to Ult(V,U)$ into a well-founded ultrapower model of $\mathrm{ZFC}$ which is isomorphic to a transitive submodel $M$ of $V$.
For a measurable cardinal $\kappa$, $M$ will itself be closed under $\kappa$-sequences from $V$, and $j(\kappa)>\kappa$.
Various niceness properties of $j(\kappa)$ (e.g. cardinality lower bounds, being a $V$-cardinal) and how ``close" $M$ is to $V$, increase the consistency strength of the large cardinal hypothesis.

% can also get *an* ultrapower by *forcing* with an ideal that gives a gen filter that is V-ultra, so gives j:VtoM in gen ext.
%   Want to investigate properties of such ultrapowers; properties of such ideals tell props of their gen ults.

Combining the method of forcing and the ultrafilter-based embedding methods allow for the construction of generic ultrapowers, where the embeddings $j:V\to M$ lie in a forcing extension of $V$.
Rather than filters, such constructions are typically phrased in terms of the dual notion of \emph{ideal}:
if $I$ is an ideal on some set algebra $\mathcal{A}$ in some $\mathcal{P}(Z)$,
then $\mathcal{A}/I$ is a valid notion of forcing which adds a filter $U$ such that every $X\in \mathcal{A}\cap V$ is either in $U$ or its complement is in $U$, and so we may construct $j:V\to Ult(V,U)$.
In the event that $\mathcal{A}/I$ only has antichains of size less than $\kappa$, then we say that $I$ is $\kappa$-\emph{saturated}.
If $\kappa\leq \card{Z}^+$, then as a result $\mathcal{A}/I$ induces a well-founded generic ultrapower and preserves a large class of cardinals.

%   
%   Now we can describe anti-saturation results.
%   Tie MS to being both a cpctness property, and an antisat result for NS.

A major theme of this thesis is \emph{anti-saturation} results, that say when an ideal is specifically \emph{not} saturated.

Solovay's Splitting Theorem for stationary sets says that the nonstationary ideal on $\kappa$ is not $\kappa$-saturated, and counts as the first major anti-saturation result for the nonstationary ideal on any regular cardinal $\kappa$.
As for other results about the non-saturation of nonstationary ideals, Gitik and Shelah showed that when $\kappa>\omega_1$, $NS_\kappa$ is not $\kappa^+$-saturated.
However, it is consistent (from very large cardinals) that $NS_{\omega_1}$ is $\omega_2$-saturated.
Likewise, for $\lambda\geq\kappa\geq\omega_1$, the nonstationary ideal on $\mathcal{P}_\kappa(\lambda)$ (for $\lambda\geq\kappa$) is known not to be $\kappa^+$-saturated. 
Burke, Foreman, Gitik, Magidor, Matsubara, and Shelah proved this over much time and many papers.

Results on \emph{any} ideal have an equally rich history, which we will cover in Section \ref{destroy_sat:background}.

In proving that the nonstationary ideal on $\mathcal{P}_{\omega_1}(\lambda)$ is not $\lambda^{\cf(\lambda)}$-saturated for any singular $\lambda$, Foreman and Magidor introduced the notion of \emph{mutually stationary} sequence, which acts as a generalization of stationarity, and of stationary reflection, for singular cardinals.

Paradoxically, although saturation results often have large cardinal consistency strength, mutual stationarity principles are a strong form of anti-saturation property and also have large cardinal consistency strength.
For instance, a Prikry generic sequence added to a measurable cardinal exhibits a mutual stationarity property, and the measurability is known to be necessary.
For mutual stationarity principles at accessible cardinals such as $\aleph_\omega$, even larger cardinals are necessary.

We now come to where this thesis's results fit into the above milieu.

Cox and Eskew have a recent anti-saturation result for  successors of regular cardinals that still guarantees many of the corollaries of saturation, such as well-foundedness of the generic ultrapower and preservation of many cardinals.
Chapter \ref{destroy_sat} generalizes their result to an inaccessible, in the form of \thref{bigthm} and \thref{savemorepresat}.

Concerning mutual stationarity, we extend the mutual stationarity result for Prikry generic sequences to Magidor generic sequences, which act to singularize a cardinal to  uncountable cofinality in a cardinal-preserving manner.
This is the content of Chapter \ref{ms}, in particular Section \ref{ms:magidor_gens}.

Finally, we develop a Magidor-like forcing $\mathbb{MC}\left(\vec{U}\right)$ that singularizes a regular cardinal $\kappa$ without collapsing $\kappa$,
and simultaneously collapses cardinals below $\kappa$ using the method of \emph{guiding generics} to turn $\kappa$ into the extended universe's $\aleph_{\omega_1}$.
This program takes up Chapter \ref{accessible_ms}, and culminates in \thref{magidor_collapse_generic_implies_geometric} and \thref{magidor_collapse_generic_iff_geometric}, which together form an exact characterization of genericity for $\mathbb{MC}\left(\vec{U}\right)$.
Given the current approaches to achieving mutual stationarity results at accessible cardinals, Magidor-like forcings along the lines of $\mathbb{MC}\left(\vec{U}\right)$ seem necessary for achieving mutual stationarity results at $\aleph_\lambda$ for $\lambda$ regular uncountable.

%   
%   Then describe the organization:
%   Preliminaries are prelims; cover basics, note interesting stuff in Mag forcing ch.
%   destroy_sat covers getting nonsat'd but still nice ideals at an inaccessible cardinal and was first my preprint on the arXiv.
%   MS chapter describes MS, and also new result that mag gens satisfy MS like Prikry gens.
%   accesssible_MS describes ongoing pf of concept project to get MS results at aleph_omega_1. Here we define and prove results about a novel Magidor-type forcing with intercoll & guide gen, incl. a proof of its charn of geny.  

The paper is organized as follows.
Chapter \ref{forcing} describes our required preliminaries, including stationary sets, the basics of forcing, ideals \& measures, Mitchell order, Prikry forcing and Prikry forcing with collapses, and Magidor forcing.
Chapter \ref{destroy_sat} first appeared on the arXiv (as \cite{schoem_destroy_sat_inaccessible}) and covers our extension of Cox and Eskew's anti-saturation result to inaccessibles, in the form of Theorem \thref{bigthm} and \thref{savemorepresat}.
Chapter \ref{ms} outlines a brief history of mutual stationarity results, expands on how mutual stationarity acts as an anti-saturation principle for nonstationary ideals, and exposits on indiscernibility-based methods pioneered by Koepke, and collated in \ref{ms:koepke}; we then cover \thref{simult_indisc_useful}, a novel simultaneous indiscernibility result that shows in \ref{ms:magidor_gens} that Magidor generic sequences exhibit mutual stationarity properties.
Finally, Chapter \ref{accessible_ms} describes a Magidor-type forcing $\mathbb{MC}\left(\vec{U}\right)$ that turns a measurable $\kappa$ into $\aleph_{\omega_1}$; we state and prove its relevant Prikry-type lemmata in \thref{magidor_collapse_prikry_open_dense} and \thref{magidor_collapse_prikry_open_dense_better} and a complete characterization of genericity in \thref{magidor_collapse_generic_implies_geometric} and \thref{magidor_collapse_generic_iff_geometric}.

In the preliminaries up through The Prikry forcing section \ref{forcing:prikry}, we state well-known results, giving proofs or sketches as needed. In the preliminary Magidor forcing section \ref{forcing:magidor}, we flesh out most proofs, as the results are sometimes only implicit in the literature.
