\section{Background}
\label{destroy_sat:background}

Besides results about nonstationary ideals discussed in Section \ref{intro}, one can also ask whether there is \emph{any} ideal on $\kappa$ that is $\kappa$-saturated, $\kappa^+$-saturated, any amount of presaturated, or even just precipitous. Results here are well-established and comprehensive.

The existence of exactly $\kappa$-saturated or $\kappa^+$-saturated ideals on inaccessible $\kappa$ are equiconsistent with a measurable cardinal.
This was first shown by Kunen and Paris in \cite{kunen_paris_measurables}, with weakly compact being compatible with $\kappa^+$-saturation (and it was known since early work of L\'evy and Silver that a $\kappa$-saturated ideal on $\kappa$ prevents $\kappa$ from being weakly compact).
Subsequently, Boos showed that an exactly $\kappa^+$-saturated ideal on $\kappa$ can exist at a non-weakly compact $\kappa$ in \cite{boos_efface_mahlo}.

As for successor cardinals, the consistency results are more striking. Certain arguments show that if $\kappa$ carries a $\kappa$-saturated ideal, then $\kappa$ must be weakly Mahlo, and hence not a successor.
Proofs can be found in \cite{baumgartner_taylor_wagon_ns_lcs} and \cite{ulam_dissertation}.
However, $\kappa^+$-saturated ideals \emph{can} occur at successor $\kappa$; the known ways to achieve this come from forcing over models with huge cardinals as done by Kunen in \cite{kunen_saturated_ideals} and Laver in \cite{laver_sat}.

Ideals on arbitrary sets $Z$ project downwards to subsets $Z'$ of $Z$, and it is natural to ask whether regularity of the inverse embedding implies nice saturation properties of the projected ideal:

\begin{question}[\cite{foreman_ideals_gen_ees}, Question 13 of Foreman]\label{foremanq13}
Let $n\in\omega$ and let $\mathcal{J}$ be an ideal on $Z\subseteq \mathcal{P}(\kappa^{+(n+1)})$.
Let $\mathcal{I}$ be the projection of $\mathcal{J}$ from $Z$ to some $Z'\subseteq \mathcal{P}(\kappa^{+n})$.
Suppose that the canonical homomorphism from $\mathcal{P}(Z')/\mathcal{I}$ to $\mathcal{P}(Z)/\mathcal{J}$ is a regular embedding.
Is $\mathcal{I}$ $\kappa^{+(n+1)}$-saturated?
\end{question}

The answer is no; prior work by Cox and Zeman in \cite{cox_zeman_antichain_catch} established counterexamples.
Later work by Cox and Eskew provided a template for finding counterexamples as follows.
We observe that $\mathcal{I}$ a $\kappa^{+n+1}$-saturated ideal on $\kappa^{+n}$ induces a wellfounded generic ultrapower and preserves $\kappa^{+n+1}$.
So we will say that an ideal $\mathcal{I}$ on $\kappa^{+n}$ is \emph{$\kappa^{+n+1}$-presaturated} if $\mathcal{I}$ induces a wellfounded generic ultrapower and preserves $\kappa^{+n+1}$.
Our template is then:

\begin{fact}[\cite{cox_eskew_kill_sat_save_presat}, corollary of Theorem 1.2]
Any $\kappa^{+n+1}$-presaturated, non-$\kappa^{+n+1}$ saturated ideal on $\kappa^{+n}$ provides a counterexample to Question \ref{foremanq13}.
\end{fact}

This makes finding presaturated, nonsaturated ideals an interesting project in its own right.

To construct such ideals for successor cardinals $\kappa=\mu^+$ (with $\mu$ regular and mild assumptions on cardinal arithmetic),
Cox and Eskew in \cite{cox_eskew_kill_sat_save_presat} generalized a forcing of Baumgartner and Taylor in \cite{baumgartner_taylor_sat_gen_ees_two} to add a club subset $C$ of $\kappa$ with $<\mu$-conditions.
(Baumgartner and Taylor's original version in \cite{baumgartner_taylor_sat_gen_ees_two} was for $\mu=\omega$.)
This $C$ prevented $\kappa^+$-saturated ideals on $\kappa$ from existing in the generic extension.
At the same time, their forcing was \emph{strongly proper}; with use of Foreman's Duality Theorem \cite{foreman_ideals_gen_ees}, a powerful tool for computing properties of ideals in generic extensions, Cox and Eskew were then able to argue that their forcing preserved the $\kappa^+$-presaturation of a large class of ideals (including $\kappa^+$-saturated ideals) in the generic extension.

This results in the following:
\begin{fact}
Let $V$ be a universe admitting $\kappa$-complete, $\kappa^+$-saturated ideals at $\kappa$ the successor of a regular cardinal. 
Then there is a forcing $\mathbb{P}$ such that $V^\mathbb{P}$ admits no $\kappa^+$-saturated ideals, however if $I$ is a $\kappa^+$-saturated ideal on $\kappa$ in $V$, then in $V^\mathbb{P}$ there is an $S\in \overline{I}^+$\footnote{where $\overline{I}$ is the ideal induced in $V^\mathbb{P}$ by $I$ and is defined by $\overline{I}=\{A\in \mathcal{P}^{V^\mathbb{P}}(\kappa) \mid \exists N\in I \ A\subseteq N\}$.}
such that $\overline{I}\upharpoonright S$ is $\kappa^+$-presaturated.
\end{fact}

It remained open as to whether the above could be done for $\kappa$ an inaccessible cardinal;
this was the content of Question 8.5 of \cite{cox_eskew_kill_sat_save_presat} and further clarifications provided in \cite{cox_schoem_overflow}.

\thref{bigthm} and \thref{savemorepresat} establish that Question \ref{foremanq13} is consistently false at $\kappa$ inaccessible, by way of partially extending the arguments and results of Theorem 4.1 of \cite{cox_eskew_kill_sat_save_presat}:

\begin{theorem}\thlabel{bigthm}
Suppose $V$ is a universe of $\mathrm{ZFC}$ with an inaccessible cardinal $\kappa$ admitting $\kappa$-complete, normal, $\kappa^+$-saturated ideals on $\kappa$ concentrating on inaccessible cardinals below $\kappa$ (i.e. such that $Inacc_\kappa\in I^+$).
Then there is a poset $\mathbb{Q}$ such that:
\begin{enumerate}[label={(\roman*)}]
\item $V^\mathbb{Q}\models``\text{there are no }\kappa\text{-complete, }\kappa^+\text{-saturated ideals on }\kappa \text{  concentrating on regular cardinals}"$ \label{bigthm:killsat}
\item If $I\in V$ is a $\kappa$-complete, normal, $\kappa^+$-saturated ideal on $\kappa$ concentrating on regular cardinals, 
then $V^\mathbb{Q}\models``\overline{I}\text{ is }\kappa^+\text{-presaturated}"$ \label{bigthm:savepresat}
\end{enumerate}
where $\overline{I}=\{A\in \mathcal{P}^{V^\mathbb{Q}}(\kappa) \mid \exists N\in I \ A\subseteq N\}$.
\end{theorem}

We can further generalize Theorem \ref{bigthm}\ref{bigthm:savepresat} as follows:

\begin{theorem}\thlabel{savemorepresat}
With the same assumptions, there is a $\mathbb{Q}$ such that if $\delta>\kappa$ is a regular cardinal, $I\in V$ is normal, fine, $\delta$-presaturated ideal of uniform completeness $\kappa$ on some algebra of sets $Z$ concentrating on inaccessible cardinals below $\kappa$ (i.e. $\{z\in Z \mid z\cap \kappa \in \kappa \text{ is inaccessible}\}$ is in its dual filter) such that
\begin{itemize}
\item $\forces_{\mathcal{B}_I} |\dot{j}_I(\kappa)|=\delta<\dot{j}_I(\kappa)$
where $\dot{j}_I$ is a name for the generic elementary embedding $j_I:V\to M$ added by $\mathcal{B}_I:=\mathcal{P}(Z)/I$;
\item $\mathcal{B}_I$ is proper on $IA_{<\delta}$;
\end{itemize}
then in $V^\mathbb{Q}$,
\begin{itemize}
\item $\overline{I}$ is not $\delta$-saturated
\item but $\overline{I}$ is $\delta$-presaturated
\end{itemize}
where $\overline{I}$ is as above.
\end{theorem}

% N.B. the above size would be computed in V[G], not in \Ult(V,I).

Here, $IA_{<\delta}$ is the collection of internally approachable structures of length $<\delta$; we will give a precise definition in Section \ref{destroy_sat:preliminaries}.

\begin{remark}
It will turn out that the same $\mathbb{Q}$ will work for both Theorem \ref{bigthm} and Theorem \ref{savemorepresat}.
\end{remark}

\begin{remark}
In \cite{cox_eskew_kill_sat_save_presat}, the analogous theorem (Theorem 4.1(2)) argued that there is an $S\in \overline{I}^+$ such that $\overline{I}\upharpoonright S$ is not $\delta$-saturated, but it is $\delta$-presaturated.

The use of such an $S$ was required there due to the forcing involved not being $\kappa$-cc.
\end{remark}

This chapter is structured as follows. 
Section \ref{destroy_sat:preliminaries} presents the preliminary definitions and facts pertinent to this paper.
Section \ref{destroy_sat:the_itern} introduces the forcing iteration $\mathbb{Q}$ of Theorems \ref{bigthm}\ref{bigthm:killsat}, \ref{bigthm}\ref{bigthm:savepresat}, and \ref{savemorepresat}.
Section \ref{destroy_sat:destroy_sat} shows that several saturated ideals are sundered from $V^{\mathbb{Q}}$.
Section \ref{destroy_sat:preserve_presat} proves that a portion of presaturated posets remain presaturated in $V^{\mathbb{Q}}$.
% Section \ref{open-qs} concludes and catalogs some conjectures.
