\section{Chapter-specific preliminaries}
\label{destroy_sat:preliminaries}

(TODO: Put the section-specific background here, i.e. stuff that's not fundamental enough to go in the intro but is only applicable to this chapter, and separate out the rest.

Especially some of the notational bs like $Reg_\kappa$, $V^{\mathbb{P}}$.

Also for subject matter: ideals, cplteness, normality, cc, presat, closure, precipitousness, generic ultrapowers, Foreman duality.)

Here are some definitions, theorems, and notations we use.

For a cardinal $\kappa$, we will write $Reg_\kappa$ for the set of regular cardinals below $\kappa$, and $cof(\kappa)$ for the proper class of cardinals of cofinality $\kappa$.

If $\mathbb{P}$ is a notion of forcing in $V$, we will variously use $V^\mathbb{P}$ or $V[G]$ to refer to the generic extension of $V$ by $\mathbb{P}$.

We will further take for granted that the reader is familiar with forcing, iterated forcing, and ultrapowers.

\begin{definition}[ideals]
Let $\kappa$ be a cardinal.
An \emph{ideal} $I$ on $\kappa$ is a subset of $\mathcal{P}(\kappa)$ such that:
\begin{enumerate}
\item $\emptyset\in I$, $\kappa\notin I$
\item If $A\in I$ and $B\subseteq A$ then $B\in I$
\item If $A,B\in I$ then $A\cup B\in I$
\end{enumerate}

For $\mu\in Reg_\kappa$, the ideal $I$ is said to be \emph{$\mu$-complete} if whenever $\lambda\in Reg_\mu$ and $\seq{A_\alpha \mid \alpha<\lambda}\subseteq I$ then
\[\bigcup_{\alpha<\lambda} A_\alpha\]
is also in $I$.

The ideal $I$ is said to be \emph{normal} if whenever $\seq{A_\alpha\mid \alpha<\kappa}\subseteq I$, we have that the diagonal union
\[\nabla_{\alpha<\kappa} A_\alpha:=\{\beta<\kappa \mid \exists \alpha<\beta \ \beta\in A_\alpha\}\]
is also in $I$.
\end{definition}

An ideal is \emph{principal} if it contains a cofinite set; for our purposes, ideals are always assumed to be nonprincipal.


For an ideal $I$ on $\kappa$, we define $I^+:=\{S\subseteq \kappa \mid S\notin I\}$.


For example, $NS_\kappa$, the collection of nonstationary sets on $\kappa$, forms a normal ideal; its dual filter is the club filter on $\kappa$, and $(NS_\kappa)^+$ is the collection of stationary sets on $\kappa$.

\begin{definition}
If $I$ is an ideal on $\kappa$ then we may define an equivalence relation $\simeq_I$ on $\mathcal{P}(\kappa)$ by $A\simeq B$ if and only if $(A\setminus B)\cup (B\setminus A)\in I$.

We say that $A\leq_I B$ if $A\setminus B\in I$.

We may consider the equivalence classes $\mathcal{P}(\kappa)/I:=\{[A]_{\simeq_I}\mid A\subseteq \kappa\}$ as a poset with partial order $\leq_I$.
\end{definition}


Given $I$ an ideal on $\kappa$, we will write $\mathcal{B}_I:=\left(\mathcal{P}(\kappa)/I\right)\setminus [\emptyset]_{\simeq_I}$; when thinking of $\mathcal{B}_I$ as a poset, we will implicitly use the partial ordering $\leq_I$ and in many cases, $\mathcal{B}_I$ will be a separative notion of forcing (or even a complete Boolean algebra).

The above two definitions are Definitions 2.1, 2.17, and 2.18\footnote{In \cite{foreman_ideals_gen_ees}, a different version of normality is taken to be definitional, and the equivalence of these two versions is Proposition 2.19 of \cite{foreman_ideals_gen_ees}.} of \cite{foreman_ideals_gen_ees}.

The following definition summarizes some forcing properties of posets that will come in handy:

\begin{definition}[Chain condition, presaturation, and closure]
Let $(\mathbb{P},\leq)$ be a poset. We say that:
\begin{enumerate}[label={(\roman*)}]
\item (\cite{baumgartner_taylor_sat_gen_ees_two}, as Theorem 4.2) $\mathbb{P}$ is \emph{$\mu$-presaturated} if for every $\lambda<\mu$ and every family $\seq{A_\alpha \mid \alpha<\lambda}$ of antichains,
there are densely many $p\in\mathbb{P}$ such that for all $\alpha$, $\{q\in A_\alpha \mid p\compat q\}$ has cardinality $<\mu$. Note that $\mu$-cc implies $\mu$-presaturation.

\item $\mathbb{P}$ is \emph{$<\kappa$-closed} if whenever $\tau<\kappa$ and $\seq{p_\alpha \mid \alpha<\tau}$ is a $\leq$-decreasing sequence in $\mathbb{P}$, there is a $p\in\mathbb{P}$ such that $p\leq p_\alpha$ for all $\alpha<\tau$

\item $\mathbb{P}$ is \emph{$<\kappa$-directed closed} ($<\kappa$-dc) if whenever $D\subseteq \mathbb{P}$ is a directed set\footnote{that is, for all $p,q\in D$, there is an $r\in D$ such that $r\leq p,q$} with $|D|<\kappa$, there is a $q\in \mathbb{P}$ such that whenever $p\in D$, $q\leq p$

\item $\mathbb{P}$ is \emph{$\mu$-preserving} (for $\mu$ a $V$-cardinal) if $V^\mathbb{P}\models ``\check{\mu}\text{ is a cardinal}"$
\end{enumerate}
\end{definition}

Some of these properties have analogues for ideals as well.
To begin with, if $I$ is a $\kappa$-complete ideal on $\kappa$ then a $\mathcal{B}_I$-generic object induces a $V$-$\kappa$-complete ultrafilter $U$ on $\kappa$ from which the ultrafilter $Ult(V,U)$ may be formed.
If $I$ is additionally normal, then $U$ will be $V$-normal.

\begin{definition}[Definition 2.4 of \cite{foreman_ideals_gen_ees}]
An ideal $I$ is said to be \emph{precipitous} if whenever $U$ is a $\mathcal{B}_I$-generic object over $V$,
$Ult(V,U)$ is well-founded.
\end{definition}

For $I$ an ideal on $\kappa$, we will say that $I$ is defined to be \emph{$\mu$-saturated} if $\mathcal{B}_I$ has the $\mu$-cc.
It is well known that a $\mu$-saturated ideal is precipitous and $\mu$-preserving, i.e. that $V^{\mathcal{B}_I}\models``\mu\text{ is a cardinal}"$.
However, we make the following caveat:

\begin{caveat}
In contrast to the above definition, an ideal $I$ is defined to be $\mu$-presaturated if $I$ is precipitous and $\mu$-preserving.

Only for precipitous ideals $I$ is it the case that $I$ is $\mu$-presaturated if and only if $\mathcal{B}_I$ is $\mu$-presaturated as a forcing poset.
\end{caveat}

Presaturation can be pushed downwards through an iteration:

\begin{lemma}[Lemma 2.12 of \cite{cox_eskew_kill_sat_save_presat}]\label{pushpresatdown}
If $\mathbb{P} * \dot{\mathbb{Q}}$ is $\kappa$-presaturated then $\mathbb{P}$ is $\kappa$-presaturated and $1_\mathbb{P}\forces \dot{\mathbb{Q}}$ is $\kappa$-presaturated.
\end{lemma}

Whether the converse holds is currently an open problem; this appears as Question 8.6 of \cite{cox_eskew_kill_sat_save_presat}. 

Next we go over the notion of properness and relate properness and closedness to presaturation.

Let $\delta$ be regular uncountable, and let $H\supsetneq\delta$.
Then we write $\mathcal{P}_\delta(H)$ for all subsets of $H$ of size $<\delta$, and $\mathcal{P}^*_\delta(H)$ to denote the set of all $x\in \mathcal{P}_\delta(H)$ such that $x\cap\delta\in\delta$.

\begin{definition}
Let $\mathbb{P}$ be a notion of forcing, $\theta$ sufficiently large so that $\mathbb{P}\in H_\theta$, and $M\prec (H_\theta,\in,\mathbb{P})$. 

We say that $p\in\mathbb{P}$ is an \emph{$(M,\mathbb{P})$-master condition} if for every dense $D\in M$, $D\cap M$ is predense below $p$; equivalently, $p\forces_{\mathbb{P}} M[\dot{G}_{\mathbb{P}}]\cap V=M$. 

Additionally, we say that $p$ is an \emph{$(M,\mathbb{P})$-strong master condition} if for every $p'\leq p$, there is some $p'_M\in M\cap\mathbb{P}$ such that every extension of $p'_M$ in $M\cap\mathbb{P}$ is compatible with $p'$. 
\footnote{It is straightforward to see that strong master conditions are also master conditions.}

Further, $\mathbb{P}$ is \emph{(strongly) proper with respect to $M$} if every $p\in M\cap\mathbb{P}$ has a $q\leq p$ such that $q$ is an $(M,\mathbb{P})$-(strong) master condition.

We say that $\mathbb{P}$ is \emph{(strongly) $\delta$-proper on a stationary set} if there is a stationary subset $S$ of $\mathcal{P}^*_\delta(H_\theta)$ such that for every $M\in S$, $M\prec (H_\theta,\in,\mathbb{P})$ and $\mathbb{P}$ is (strongly) proper with respect to $M$.
\end{definition}

Note that $\{M\in \mathcal{P}^*_\delta(H_\theta)\mid M\prec (H_\theta,\in,\mathbb{P})\}$ is a club subset of $\mathcal{P}^*_\delta(H_\theta)$; so a forcing being $\delta$-proper on a stationary set really only depends on the properness condition.

\begin{fact}
If $\mathbb{P}$ is $\delta$-proper on a stationary set, then $\mathbb{P}$ is $\delta$-presaturated.
\end{fact}

This fact appears as Fact 2.8 of \cite{cox_eskew_kill_sat_save_presat}, with proof; their proof, in turn, generalizes a result of Foreman and Magidor in the case of $\delta=\omega_1$ (namely, Proposition 3.2 of \cite{foreman_magidor_lcs_ctx_ch}).

For the posets we will be working with, we will have a specific stationary subset witnessing $\delta$-properness:

\begin{definition}
For $\delta$ regular and $\theta>>\delta$, we say that $IA_{<\delta}\subseteq \mathcal{P}^*_\delta(H_\theta)$, 
the ``internally approachable sets of length $<\delta$", 
is the collection of all $M\in \mathcal{P}^*_\delta(H_\theta)$, with $|M|=|M\cap \delta|$, that are \emph{internally approachable},
i.e. such that there is a $\zeta<\delta$ and a continuous $\subseteq$-increasing sequence $\seq{N_\alpha\mid \alpha<\zeta}$ whose union is $M$, such that $\vec{N}\upharpoonright \alpha\in M$ for all $\alpha<\zeta$.
\end{definition}

In a sense, internal approachability is preserved by any generic extension:

\begin{fact}\label{principle-A}
Suppose $\mathbb{P}$ is a poset, $M\prec(H_\theta,\in,\mathbb{P})$, $\seq{N_\alpha\mid\alpha<\zeta}$ witnesses that $M\in IA_{<\delta}$, and $G$ is $(V,\mathbb{P})$-generic.
Then in $V[G]$, $\seq{N_\alpha[G]\mid \alpha<\zeta}$ witnesses that $M[G]\in IA_{<\delta}$. (Without loss of generality, we may assume that $\mathbb{P}\in N_0$.)
\end{fact}

It is a standard fact that $IA_{<\delta}$ is stationary.
The following lemma makes clear its utility:

\begin{lemma}\label{lemma-iaposets}
Let $\delta$ be regular and uncountable. Then:
\begin{enumerate}[label={(\roman*)}]
\item\label{lemma-iaposets:cc}
If $\mathbb{P}$ is $\delta$-cc and $M\prec (H_\theta,\in,\mathbb{P})$ is an element of $\mathcal{P}^*_\delta(H_\theta)$ (i.e. if $M\cap\delta\in\delta$), then $1_\mathbb{P}$ is an $(M,\mathbb{P})$-master condition; in particular $\mathbb{P}$ is $\delta$-proper on $\mathcal{P}^*_\delta(H_\theta)$.

\item\label{lemma-iaposets:closed}
If $\mathbb{Q}$ is $<\delta$-closed then $\mathbb{Q}$ is $\delta$-proper on $IA_{<\delta}$.

\item\label{lemma-iaposets:iter}
If $\mathbb{P}$ is $\delta$-proper on $IA_{<\delta}$ and $\forces_\mathbb{P}``\dot{\mathbb{Q}}\text{ is }\delta\text{-cc}$ or $\forces_\mathbb{P}``\dot{\mathbb{Q}}\text{ is }<\delta\text{-closed}$ then $\mathbb{P}*\mathbb{\dot{Q}}$ is $\delta$-proper on $IA_{<\delta}$.
\end{enumerate}
\end{lemma}

This is roughly Fact 2.9 out of \cite{cox_eskew_kill_sat_save_presat}. The following proof is largely reproduced from \cite{cox_eskew_kill_sat_save_presat} as well.

\begin{proof}
For part \ref{lemma-iaposets:cc}, let $A\in M$ be a maximal antichain in $\mathbb{P}$.
Since $|A|<\delta$ and $M\cap\delta\in\delta$, we have that $A\subseteq M$.
Thus $1_\mathbb{P}\forces M[\dot{G}]\cap\check{V}=M$, so $1_\mathbb{P}$ is a master condition for $M$.

Part \ref{lemma-iaposets:closed} is due to Foreman and Magidor in \cite{foreman_magidor_lcs_ctx_ch}. %I can't specifically find it here, but Cox & Eskew say it's in there.

As for part \ref{lemma-iaposets:iter}, let $G$ be $\mathbb{P}$-generic over $V$.
Suppose that $M\prec (H_\theta,\in,\mathbb{P}*\dot{\mathbb{Q}})$ and $M\in IA_{<\delta}$.
By Fact \ref{principle-A}, combined with \ref{lemma-iaposets:cc} and \ref{lemma-iaposets:closed},
$\mathbb{P}$ forces that $\dot{\mathbb{Q}}$ is proper with respect to $M[\dot{G}]$.
Hence $\mathbb{P}*\dot{\mathbb{Q}}$ is proper with respect to $M$.
\end{proof}

Presaturation has a useful corollary:
\begin{fact}
If $\mathbb{P}$ is $\lambda$-presaturated for $\lambda$ regular then 
\[\forces_{\mathbb{P}} cof^V(\geq\lambda)=cof^{V[\dot{G}]}(\geq\lambda)\]
\end{fact}
The above fact has a partial converse. We will not make use of it, but it is another known way to argue that certain iterations of presaturated forcings are presaturated:
\begin{fact}\label{cof->presat}
If $\mathbb{P}$ is $\lambda^{+\omega}$-cc for some regular $\lambda\geq\omega_1$ and
\[\forall n\in\omega \ \forces_{\mathbb{P}} cf^{V[\dot{G}]}\left(\left(\lambda^{+n}\right)^V\right)\geq\lambda\]
then $\mathbb{P}$ is $\lambda$-presaturated.
\end{fact}

This appears as Fact 2.11 in \cite{cox_eskew_kill_sat_save_presat}, which in turn is a generalization of Theorem 4.3 of \cite{baumgartner_taylor_sat_gen_ees_two}.

\begin{fact}\label{foreman_ideals_gen_ees:ultrapower-closure}
For a $\kappa$-complete, $\kappa^+$-saturated ideal $I\in V$,
if $U$ is a $\mathcal{B}_I$-generic filter over $V$
then in $V[U]$, $^\kappa Ult(V,U)\subseteq Ult(V,U)$; that is, $Ult(V,U)$ is closed under $\kappa$-sequences from $V[U]$.
\end{fact}

This follows from Propositions 2.9 and 2.14 of \cite{foreman_ideals_gen_ees}.


We will sometimes write $Ult(V,I)$ to denote $Ult(V,U)$, and will also write $j_I$ to denote $j_U:V\to Ult(V,U)$.

If $I\in V$ is an ideal on $\kappa$ and $\mathbb{P}$ is a notion of forcing understood from context, then we will write $\overline{I}:=\left\{N\in \mathcal{P}^{V^\mathbb{P}}(\kappa)\mid \exists A\in I \ N\subseteq A\right\}$.

The following two simplified versions of Foreman's Duality Theorem will be useful later:

\begin{lemma}\label{foreman_ideals_gen_ees:groundideals}
For a $\kappa$-complete, $\kappa^+$ saturated $I\in V$, $\overline{I}$ is $\kappa^+$-saturated in $V^\mathbb{Q}$ if and only if $\forces_{\mathcal{B}_I} \dot{j}_I(\mathbb{Q})$ is $\kappa^+$-cc.
\end{lemma}
 
This appears as Corollary 7.21 in \cite{foreman_ideals_gen_ees}.

\begin{theorem}
\label{easyduality}
Let $I$ be a $\kappa$-complete normal precipitous ideal in $V$ and $\mathbb{Q}$ be a $\kappa$-cc poset. 
Then $\overline{I}$ is precipitous and there is a canonical isomorphism witnessing that
\[\mathcal{B}\left(\mathbb{Q} * \mathcal{B}_{\overline{I}}\right)\cong \mathcal{B}\left(\mathcal{B}_I * \dot{j}_I\left(\mathbb{Q}\right)\right)\]
where $\mathcal{B}(\mathbb{P})$ refers to the Boolean completion of $\mathbb{P}$.
\end{theorem}

This statement appears in \cite{cox_eskew_kill_sat_save_presat} as Fact 2.24, and is a corollary of Theorem 7.14 of \cite{foreman_ideals_gen_ees}.
