\section{Destroying Saturation}
\label{destroy_sat:destroy_sat}

Since $\mathbb{Q}$ projects to each $\mathbb{Q}_\mu * \dot{\mathbb{P}}(\mu)$, $\mu<\kappa$ inaccessible, we may, for each such $\mu$, let $G_\mu$ be the restriction of the $\mathbb{Q}$-generic $G$ to $\mathbb{P}(\mu)$ and define 
$C_\mu=\{\xi \mid \exists (s,f)\in G_\mu \ \xi\in s\}$.
By Lemma \ref{pmuisnice}\ref{pmuisnice:club}, $C_\mu$ is a club subset of $\mu^+$ in $V^{\mathbb{Q}_{\mu}*\dot{\mathbb{P}}(\mu)}$ and for every $X\in V^{\mathbb{Q}_{\mu}}$ such that $X\subseteq [\mu,\mu^+)$ and $X$ has $V^{\mathbb{Q}_{\mu}}$-cardinality $\geq\mu$, $X\not\subseteq C_\mu$. 

As a warmup to proving Theorem \ref{bigthm}\ref{bigthm:killsat}, we argue the following:

\begin{proposition}\label{ground-killsat}
Suppose that $I\in V$ is $\kappa$-complete, normal, $\kappa^+$-saturated, and concentrates on $Inacc_\kappa$. 
Then in $V^\mathbb{Q}$, $\overline{I}$ is not $\kappa^+$-saturated.
\end{proposition}

Before we prove this, it will be helpful to isolate a lemma on what $j_I(\mathbb{Q})$ looks like in $\Ult(V,I)$:

\begin{lemma}\label{jQ-ultVI}
Let $I$ be a $\kappa$-complete, normal, fine precipitous ideal concentrating on inaccessibles.
Then in $\Ult(V,I)$, 
$j_I(\mathbb{Q})\cong \mathbb{Q}*\dot{\mathbb{R}}$, where $\dot{\mathbb{R}}$ is a name for an Easton support iteration $\seq{\mathbb{R}_\lambda * \dot{\mathbb{C}}(\lambda) \mid \lambda\in[\kappa,j(\kappa))}$, such that if $\lambda$ is $Ult(V,I)$-inaccessible, $\mathbb{C}(\lambda)=\mathbb{P}(\lambda)$, and $\mathbb{C}(\lambda)$ is the trivial forcing otherwise.
\end{lemma}

And we remark on how $\Ult(V,I)$ computes $\kappa^+$:

\begin{lemma}
  Let $I$ be as in Lemma \label{jQ-ultVI}, with $G$ a $\mathcal{B}_I$-generic over $V$.
  Then if $I$ is $\kappa^+$-saturated, then $(\kappa^+)^{\Ult(V,I)}=(\kappa^+)^{V[G]}$.
\end{lemma}

Thus for $\kappa^+$-saturated ideals, we will just write $\kappa^+$ to mean $(\kappa^+)^V=(\kappa^+)^{V[G]}=(\kappa^+)^{\Ult(V,I)}$.

\begin{proof}
  Since $I$ is $\kappa^+$-presaturated, forcing with $\mathcal{B}_I$ preserves $\kappa^+$, hence $(\kappa^+)^V=(\kappa^+)^{V[G]}\geq (\kappa^+)^{\Ult(V,I)}$.
  
  To see that $(\kappa^+)^{V[G]}=(\kappa^+)^{\Ult(V,I)}$, 
  suppose that $\alpha\in [\kappa,(\kappa^+)^{V[G]})$.
  Let this be witnessed by some $\kappa$-sequence $f:\kappa\to\alpha$ a bijection.
  Since $I$ is $\kappa^+$-saturated, we have from Fact \ref{foreman_ideals_gen_ees:ultrapower-closure} that $\Ult(V,I)$ is closed under $\kappa$-sequences from $V[G]$, and so $f\in Ult(V,I)$.
  Thus $\alpha$ is not a cardinal in $Ult(V,I)$.
\end{proof}

\begin{proof}
This follows from the elementarity of $j_I$, and since $I$ concentrates on inaccessibles, $\kappa$ is inaccessible in $\Ult(V,I)$.
\end{proof}

\begin{remark}
As with ultrapowers from a measurable cardinal, we will have that if $I$ is a $\kappa$-complete normal precipitous ideal in $V$, then in $V^{\mathcal{B}_I}$, $|j_I(\kappa)|=2^\kappa$.
However, by elementarity, in $\Ult(V,I)$, $j_I(\kappa)$ is inaccessible.
\end{remark}

\begin{remark}
This is unlike a $\lambda$-complete, $\lambda^+$-saturated ideal $J$ on $\lambda$ a successor cardinal;
for $\lambda$ a successor cardinal, we would have that $j_J(\lambda)=\lambda^+$. The argument can be found in \cite{foreman_ideals_gen_ees}.
\end{remark}

\begin{proof}[Proof of Proposition \ref{ground-killsat}]
By Lemma \ref{jQ-ultVI}, in $V^{\mathcal{B}_I}$, $\dot{j}_I(\mathbb{Q})\cong \mathbb{Q}*\dot{\mathbb{R}}$, where $\dot{\mathbb{R}}$ is an Easton support iteration $\seq{\mathbb{R}_\lambda * \dot{\mathbb{C}}(\lambda) \mid \lambda\in[\kappa,j_I(\kappa))}$ as in the lemma.

Since $I$ concentrates on inaccessibles below $\kappa$,
$\kappa$ is still inaccessible in $\Ult(V,I)$.
Thus $\mathbb{C}(\kappa)=\mathbb{P}(\kappa)$ which is not $\kappa^+$-cc. 
So $j_I(\mathbb{Q})$ is not $\kappa^+$-saturated.

So by Lemma \ref{foreman_ideals_gen_ees:groundideals}, in $V^\mathbb{Q}$, $\overline{I}$ is not $\kappa^+$-saturated.
\end{proof}

We now prove Theorem \ref{bigthm}\ref{bigthm:killsat}.

\begin{proof}[Proof of Theorem \ref{bigthm}\ref{bigthm:killsat}]
Let $G$ be $\mathbb{Q}$-generic, and suppose that in $V[G]$ there is a $\kappa$-complete, $\kappa^+$-saturated ideal $\mathcal{J}$ on $\kappa$ concentrating on inaccessible cardinals below $\kappa$.

Let $U$ be $P(\kappa)/\mathcal{J}$-generic over $V[G]$, and let $j:V[G]\to \Ult(V[G],U)$ be the generic ultrapower.

Let $N=\bigcup_{\alpha\in ORD} j(V_\alpha)$. Then $j(\mathbb{Q})\in N$ and hence $\Ult(V[G],U)=N[g']$ for some $g'\in V[G*U]$ which is $j(\mathbb{Q})$-generic over $N$.

Observe that $\kappa$ is still inaccessible in $N[g']$ by inaccessibility in $V[G]$, by being the critical point of $j$, and since $\mathcal{J}$ concentrates on inaccessibles.
Since $j(\kappa)>\kappa$ and $j(\kappa)$ is a cardinal in $N[g']$, $j(\kappa)> (\kappa^+)^{N[g']}\geq (\kappa^+)^{V[G]}$ (by $\kappa$-closure and $\kappa^+$-saturation of $\mathcal{J}$).
Further, by the usual ultrapower argument, $|j(\kappa)|= 2^\kappa$. 

So $j(\kappa)$ is not a cardinal in $V$, but by Fact \ref{foreman_ideals_gen_ees:ultrapower-closure}, $N[g']$ is closed under $\kappa$-sequences from $V[G]$.

Work in $N[g']$. Let $g'$ be the projection of $j(\mathbb{Q})$ to $\mathbb{P}(\kappa)$, and let 
\[C_\kappa=\bigcup_{(s,f)\in g'} s\]
Then
\begin{equation}\label{eqn:ng'defc}
N[g']\models C_\kappa\text{ is club in }\kappa^+ \text{ and } \forall  X \in N |X|^N\geq\kappa, \ X \not\subseteq C_\kappa
\end{equation}

Since $V[G*U]$ is a $\kappa^+$-cc extension of $V$, we may let $D\in V$ be such that in $V[G*U]$, $D$ is a club subset of $C_\kappa$. 
Let $E\subseteq D$ be in $V$, $(o.t.(E))^V=\kappa$, $\alpha=\sup E$; since $cf(\alpha)=\kappa$, let $\phi:\kappa\to\alpha$ be a normal increasing sequence.

Let $E'=lim(E)\cap ran(\phi)$.

Then $E'\subseteq D$ and $|E'|^V=\kappa$ since $\kappa$ is inaccessible.
Further, $j(\phi)\in N$ and $j(\phi)\upharpoonright \kappa:\kappa\to j"\alpha$ is also in $N$.

Thus $ran(j(\phi)\upharpoonright \kappa)\in N$ and $j"E'\subseteq ran(j(\phi)\upharpoonright \kappa)\subseteq j"\alpha$.

But $j"E'=ran(j(\phi)\upharpoonright \kappa) \cap j(E')\in N$; and since $E'=\{\beta\in ran(\phi)\mid j(\beta)\in j(E')\}$, we have that $E'$ is a subset of $C_\kappa$ with $|E'|^N=\kappa$ and $E'\subseteq[\kappa,\kappa^+)$. 

This contradicts \ref{eqn:ng'defc}, and hence $\mathcal{J}$ cannot be $\kappa^+$-saturated.
\end{proof}
